Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-14 Article/ici_submm_cloudcorr.tex

%% 2-column papers and preprints
\documentclass[amt]{copernicus}

@@

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization. 
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.

\subsection{ICI simulations}
\label{sec:arts_simulations}
%

**** Some parts copied directly from AWS report *****

\subsection{Simulation dataset}
%
Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI frequency. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land. It is also assumed that all simulations are remapped to a common foorprint.

**** show any comparsion to ATMS? or AWS channels ? ****

\subsection{QRNN}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN).

\subsubsection{Model selection}
%
\label{model_selection}
A high performing QRNN model requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-paramter tuning. In grid search, different combinations of hyperparamters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. The model evaluation metrics employed in this article are described in the next section.

For the structural parameters, the grid search is performed to determine the number of neurons (width) and hidden layers (depth). The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over the validation set. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs, decay. The best performing hyperparameter configurations for a particular training set need not be same for other datasets. Therefore for each QRNN model used in this article, the hyperparameters were tuned distinctly.

@@

\section{Cloud correction in  183 GHz channels}
%
\subsection{Training data}
%
Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.
It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution. In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
\subsection{Training}
\label{sec:ici_trainin}
%t
\begin{table}[t]
\caption{Summary of the different QRNN models used in the study.}
\label{tab:QRNN_models}
\begin{tabular}{lll}
\tophline
QRNN model & Training inputs & Target \\
\middlehline
QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\

\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table}
To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed. In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.

In the first model, the training set includes the target 183\,GHz channel and the sub-mm channels. For example, to train for channel I1V, the input channels are I1V, I5V , I6V, I7V, I8V, I9V, I10V, I11V. A separate QRNN model is trained for each of the 183\,GHz channels. We shall refer this QRNN model as ``QRNN-simple''. In the second QRNN model, we suggest to use all three 183\,GHz channels (from ICI) concurrently, along with sub-mm channels. In this case, although the input training parameters are identical for all channels, the target channel is different and QRNN has to be trained separately for each. Further in text, we refer this model as ``QRNN-all''. Table~\ref{tab:QRNN_models} summarises the two QRNN models.

Apart from these two models, we also extend QRNN-simple to predict the clear-sky values for MWI channels. In this case, we combine the measurements from MWI-15(MWI-16) and the sub-mm channels to predict MWI-15(MWI-16). Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.

As described in section \ref{model_selection}, a grid search was implemented to select the best performing hyperparamters. The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:model_selection}. The results are for QRNN-simple with I3V as target channel. Increasing the complexity of the network by increasing the layer-width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-simple. For the optimising the training paramters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. We did not optimise the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.

For QRNN-all a grid search (results not shown) over width and depth and learning rates resulted in similar performance, and an identical neural network was selected.

\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
	\label{fig:}	
\end{figure}

\subsection{Results}
%
%f 
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure}
%f 
\begin{figure}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure}

%t
\begin{table}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V. Results from both QRNN-simple and QRNN-all are shown. The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:error_statistics_ici}
%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-simple} & \multicolumn{3}{c}{QRNN-all}\\
		\cline{3-10}
%		\hline
		&&   Clear-sky &   All-sky &   All &   Filtered(5K) & Filtered(15K) & All &   Filtered(5K) & Filtered(15K) \\
		\middlehline
%		\multicolumn{7}{c}{Channel - I1V}\\

Channel I1V &Bias     &   -0.00 &   -1.90&    -0.03 &      0.00(6.40\%) & 0.01(3.09\%)&-0.01 &0.01 (6.42\%)& 0.02(3.09\%) \\
			&MAE      &    0.64 &    2.35&     0.69 &      0.60 & 0.63  &  0.65 & 0.62& 0.60\\
			&STD      &    0.80 &    8.92&     1.05 &      0.78 &  0.84 &  0.97 & 0.84& 0.80\\
			&Skewness &   -0.01 &   -7.99&    -1.24 &     -0.44 & -0.48 & -0.36 &-0.51&-0.34\\
\middlehline
Channel I2V	&Bias     &   -0.00 &         -1.05 &    0.02 &      0.03(3.70\%)&0.02(1.60\%) &  0.02&   0.03(3.67\%)& 0.02(1.60\%)\\
			&MAE      &    0.64 &          1.54 &    0.56 &      0.50&  	  0.52 &  0.46&   0.42 &  0.52\\
			&STD      &    0.80 &          5.98 &    0.86 &      0.64&  	  0.69 &  0.70&   0.53 &  0.69\\
			&Skewness &    0.02 &        -10.64 &   -2.25 &     -0.22& 		 -0.58 & -1.69& -0.25 &-0.56\\
\middlehline	
Channel I3V &Bias     &   0.00  &         -0.63 &    0.02 &      0.02(2.18\%)&0.03(0.92\%)&	 0.04 &  0.04(2.18\%) & 0.04(0.92\%) \\
			&MAE      &   0.64  &          1.14 &    0.54 &      0.50		& 0.52&0.48 &    0.44 & 0.46\\
			&STD      &   0.80  &          4.26 &    0.80 &      0.64		& 0.68&0.71 &     0.56 & 0.60\\
			&Skewness &   0.00  &        -13.26 &   -1.40 &     -0.16		&-0.61&-1.41&   -0.11 & -0.77\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

%t
\begin{table}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
	\label{tab:statistics_mwi}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &   		 All &   Filtered(5\,K) & Filtered(15\,K) \\
		\middlehline
 MWI-15 		&Bias     &    0.00 &         -1.19 &           -0.02 &                -0.01(4.41\%) & -0.02(1.87\%)\\
				&MAE      &    0.64 &          1.66 &            0.56 &                 0.49 		 &  0.52\\
				&STD      &    0.80 &          6.21 &            0.84 &                 0.64 		 &  0.69\\
				&Skewness &   -0.02 &         -9.87 &           -1.67 &                -0.29 		 & -0.47\\
		\middlehline
 MWI-16 		& Bias 	   &    0.00 &         -0.80 &           -0.04 &   -0.03(2.85\%) & -0.04(1.15\%)\\
				& MAE      &    0.64 &          1.31 &            0.54 &     0.49		 & 0.51\\
				& STD      &    0.80 &          5.01 &            0.82 &     0.63		 & 0.67\\
				& Skewness &    0.01 &        -12.04 &           -1.94 &    -0.23		 &-0.81\\
		\bottomhline			
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. The prediction errors are calculated as the deviation of the predictions to their corresponding noise-free clear-sky values. We calculate the mean bias, mean absolute error and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. In the next sections, we describe the performance of the two QRNN models for ICI and MWI channels.

\subsection{Prediction accuracy}
%
The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}. The distributions of corresponding clear-sky simulations are also plotted as reference. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.

For a quantitative evaluation of how accurate the predictions are, the  deviations of the median values to the clear-sky simulations are computed. Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels. The distribution of noise is also plotted for reference. The error metrics corresponding to these results are provided in Table~\ref{tab:error_statistics_ici}. Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias among the deviations. Among the three channels, the highest cloud impact is seen in channel I1V. The average bias in channel I1V measurements is -1.89\,K, however the QRNN-single predictions successfully reduces the average deviation to -0.03\,K. The predictions and the observations have a good agreement for the main peak of the distribution, albeit the prediction errors have a sharper peak and a larger spread.  The large spread is representative of the few cases which are either under/over predicted. If all the cases with correction greater than 5\,K are excluded, only a fraction of the total cases (6.42\%) are removed but the variability in predictions errors reduces significantly. This indicates that few cases with high cloud impact could be difficult to train and predict.

>>>>

%% 2-column papers and preprints

\documentclass[amt, manuscript]{copernicus}
%\documentclass[amt]{copernicus}

%\documentclass[amt]{copernicus}

@@

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}

	\belowtable{} % Table Footnotes
\end{table*}

Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization.

\subsection{MicroWave Imager}
%
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_channels}.

\subsection{Artic Weather Satellite}
%
\begin{table*}[t]
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\label{tab:specifications_AWS}	
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
		& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
		AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

\subsection{QRNN}
%
The neural network training is a process of learning to predict the outputs {$y_i$} from inputs {$x_i$} through a series of learnable transformations. While training, neural networks seek to minimise the model error through a loss function. The choice of the loss function depends on the predictive problem. When a neural network is trained to minimise the mean of the quantile loss function to predict the quantiles of the distribution, it is called a Quantile Regression Neural Network (QRNN). 
\subsubsection{Theory}

@@

\subsection{Simulations}
\label{sec:arts_simulations}
%
\subsubsection{Input data}
%
\subsubsection{Simulation setup}
%
**** Some parts copied directly from AWS report *****

\subsection{Produced dataset}
%
Using the simulation setup described in previous section, Cloudsat profiles during August 2015 were randomly selected to generate 200\,000 cases for each ICI and MWI frequency. The input data were restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios were simulated, and no differentiation was made between the observations over ocean/sea and land. It is also assumed that all simulations of ICI and MWI are remapped to a common foorprint.

For AWS, 24 monochromatic frequencies were simulated so that each channel could be represented with sufficient accuracy. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) were simulated, but the results described in this section are based on nadir viewing angle. 130\,000 cases based on randomly selected CloudSat orbits were simulated.

\begin{table*}[t]
	\caption{Summary of the different QRNN models used in the study.}
	\label{tab:QRNN_models}
	\begin{tabular}{lllll}
		\tophline
		QRNN model & Sensor & Target & Input 183\,GHz channel &Other training inputs \\
		\middlehline
		QRNN-single &  ICI 	& I1V/I2V/I3V 	& I1V/I2V/I3V, & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{2-5}
					&  MWI 	& MWI-15/MWI-16 & MWI-15/MWI-16	& I5V, I6V, I7V, I8V, I9V, I10V, I11V \\
		\cline{2-5}
					& AWS	& AWS-32/AWS-33/ &  AWS-32/AWS-33/ & AWS-41, AWS-42, AWS-43, AWS-44\\
					&		& AWS-34/		 &	AWS-34/		   & \\
					&		& AWS-35/AWS-36	 & AWS-35/AWS-36,  &\\
		\cline{1-5}
		QRNN-all &  ICI 	& I1V/I2V/I3V 	& I1V, I2V, I3V & I5V, I6V, I7V, I8V, I9V, I10V, I11V\\
		\cline{1-5}
		QRNN-mwi &  MWI		& MWI-14/MWI-15/ &  MWI-14, MWI-15, & None 	\\	
				 &			& MWI-16/		 &  MWI-16, & \\
				 &			& MWI-17/MWI-18	 &  MWI-17, MWI-18  &\\					
	\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table*}

\subsection{Training data}
%
The QRNN models presented in this study are trained with simulated brightness temperature data to predict the noise-free clear-sky values for 183\,GHz channels. No other data was included in the training process, but the training set varied according to the QRNN-model (described further). Out of the 220\,000 simulations for ICI and MWI each, 175\,000 cases were randomly picked to form the training set. The rest were used for testing. For AWS a slightly smaller database was selected. Out of 130\,000 simulations, 100\,000 were used for training while the rest formed the testing set.

In the training set for all three sensors, 90\% of the data was randomly selected to form the training set, while the other 10\% formed the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise was added to the input training data according to the channel NE$\Delta$T. The target training data was kept noise free. In order to build a robust learning network, random noise was added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data was also normalized with mean and standard deviation.

\subsection{QRNN model configurations}
%
\label{QRNN_models}
Multiple QRNN models were trained with several combinations of the training input. For each combination, the target was always one of the available 183\,GHz channels, and this target channel was always included in the training set. The choice of other channels in the training set depended on the type of QRNN model chosen. Three main types of QRNN models were used in this study.

In the first model, the training inputs always contained data from the target 183\,GHz channel, and one or more available sub-mm channels. No data from other 183\,GHz channels was included in training. We refer this model as ``QRNN-single''. For ICI and MWI, the available sub-mm channels are 325\,GHz, 448\,GHz and 664\,GHz, while for AWS only 325\,GHz is available. It should be noted that though MWI does not have any sub-mm channels,  sub-mm channels from ICI were used. It is assumed for the simulations that data from ICI and MWI channels are mapped to a common footprint and resolution. In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.

The second model was defined to investigate the  impact of using all 183\,GHz channels concurrently. This model is referred as ``QRNN-all''. In this model, the training set included data from all available 183\,GHz channels, along with other sub-mm channels. This model was applied only to ICI. It should be noted that although the training set was identical for I1V, I2V and I3V, a separate training was needed for each channel as target.

The third model was  used only for MWI channels. In this case, all 183\,GHz channels were used concurrently in the training set. No other data from sub-mm channels was used. Further in the text, we shall refer this model as ``QRNN-mwi''.

A summary of the three QRNN models described in this study is provided in Table~\ref{tab:QRNN_models}.

\section{Results}
\subsection{QRNN network structure}
%
A high performing QRNN model requires tuning of multiple hyper-parameters. These parameters determine the structure and the training set-up of the neural network. Several of these hyper-parameters are non-learnable, and must be defined before beginning of every training. Grid search is one of the most often employed techniques for hyper-parameter tuning. In grid search, different combinations of hyper-parameters are selected and for each, the model performance is evaluated. The model architecture with the best performance is selected. We use quantile loss and CRPS for evaluation of the model performance.

For the structural parameters, the usually a grid search over the number of neurons (width) and hidden layers (depth) is performed. The model is trained for multiple values of layer widths and hidden layers, and the best configuration is selected by evaluating the predictions over validation dataset. Similarly, the training process is optimized by performing a grid search different training parameters such as : batch size, learning rate, number of epochs etc. In this study, all possible hyper-parameters were not tested. We investigated the performance of QRNN only to certain hyper-parameters like number of neurons, hidden layers, learning rate, convergence epochs and batch size. The others were chosen empirically.

Firstly, we performed a grid search to select the size of the neural network. We evaluated the performance for three sizes of hiddden layers($n_h$ = 2, 3, 4), and layer widths of sizes in the set [8, 16, 32, 64, 128, 256, 512]. The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:grid_search}. The results are for QRNN-single with I2V as target channel. Increasing the complexity of the network by increasing the layer width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-single. For the optimising the training parameters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. In order to select the batch size, we simply compared the performance for batch size = 128 and 256, and the former gave better results. Concerning number of maximum epochs, we obtained best results when the network was trained longer. Choosing a lower value of epochs (e.g. 50), did not affect the accuracy of the median value, yet deteriorated the prediction uncertainty. We did not optimise the type of activation function and Rectified Linear Unit (ReLu) was used in all layers.

Though these set of hyper-parameters were selected for QRNN-single applied to I2V, they worked well for other channnels and QRNN-all/QRNN-mwi as well. In the end, all the results described in this study use an identical  hyper-parameter configuration.

\begin{figure*}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
	\label{fig:grid_search}	
\end{figure*}

\subsection{ICI}
\subsubsection{Example results}
%
QRNN predictions are estimates of the posterior distribution over different quantiles. For this study we chose quantiles, $x_{\tau}$: median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The quantiles are interpreted as probabilitic predictions and can be used to construct a probability distribution of the predictions. This is in sharp contrast to correction approaches which give out only point estimates. As an example, Fig.~\ref{fig:posterior_distribution_I2V} shows the posterior distribution obtained from QRNN for three different cases. These results are from QRNN-single for channel I2V. The three cases shown in the figure have almost a similar median value but very different spread. The spread of the distributions can also be expressed as the prediction interval. If $y_{\tau_2}, y_{\tau_1}$ are the predictions at two quantile levels $\tau_1$ and $\tau_2$ respectively, the interval $[y_{\tau_2}, y_{\tau_1}]$ is called the prediction interval. It is gives the range where the prediction could be located and its length is a measure of the reliability. Among the three cases shown in the figure, the blue curve has shortest prediction interval indicating a sharp probabilistic prediction or more reliability. While the other two cases have longer intervals implying higher fluctuations, or low reliability.

The quantiles can also be used to  interpret the confidence intervals. For a given case, if two quantiles $\tau_1$ and $\tau_2$ are chosen, then there is $\tau_2 - \tau_1$ chance that the true value ($y_o$) shall lie in in range $[y_{\tau_1}, y_{\tau_2}]$. For example, in a 94\% confidence interval where, $\tau_1 = -2\sigma$ and $\tau_1 = +2\sigma$, there is 0.3\% probability that $y_\circ > y_{\tau_2}$, and 97\% probability that $y_\circ$ > $y_{\tau_1}$.

%f
\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/posterior_distribution_I2V.pdf} 
	\caption{Posterior distribution obtained from QRNN-single (channel I2V) for three different cases. }
	\label{fig:posterior_distribution_I2V}	
\end{figure}

\subsubsection{Error of best estimate}
%
%f
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure*}
%f 
\begin{figure*}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure*}

%t
\begin{table*}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V. Results from both QRNN-simple and QRNN-all are shown. The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:error_statistics_ici}
%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-single} & \multicolumn{3}{c}{QRNN-all}\\
		\cline{3-10}
%		\hline
		&&   Clear-sky &   All-sky &  Filtered & Predicted & Predicted &   Filtered & Predicted & Predicted \\
		&&&&							(5\,K) &(All)& (5\,K) & (5\,K)&(All)& (5\,K)\\
		\middlehline
%		\multicolumn{7}{c}{Channel - I1V}\\
